### 2017-01-18 thesis/methods/methods.tex
Finished pathway enrichment analysis section

For a given list of differentially expressed genes identified in a data set, the \texttt{camera} function from the \textit{limma} package was used to identify the pathways that were enriched in those genes.
The \gls{go} database was used to identify the enriched pathways.

>>>>

\Gls{ontology} is defined as a set of concepts and categories in a subject area or domain that shows their properties and the relations between them.
\Acrfull{go}, as the name suggests, is an \gls{ontology} of the genes and biological pathways, curated and maintained by the \gls{go} Consortium \citep{GO2000,GO2004}.
The goal of the \gls{go} Consortium is to ``produce a structured, precisely defined, common, controlled vocabulary for describing the roles of genes and gene products in any organism'' \citep{GO2000}.
The \gls{go} database includes not only the human genetic information, but collates variety of information from eukaryotic cells, including \textit{Arabidopsis thaliana} and \textit{Drosophila melanogaster} \citep{GO2000,GO2004}.

\gls{go} provides three distinct ontologies to describe the role of a gene or its gene product in the cell: biological process, molecular function, and cellular component \citep{GO2000}.
Biological process categorises the genes or its gene products into their overarching biological purpose or goal in the cell; for example, ``cell death'' and ``cell growth and maintenance''.
Molecular function describes the biochemical activity a gene or protein has, ignoring when or where the activity takes place.
The definition of ``biochemical activity'' is very broad as it includes specific binding to ligands and structure.
Examples of terms used in molecular function are ``kinase activity'', ``transporter'' and ``ligands''.
Lastly, cellular components refers to the location in which the gene product is active, such as ``Golgi apparatus'' and ``nuclear membrane''.

Due to the sheer amount of terms and definitions available from the data, \gls{go} was chosen as the database for pathway reference.
The \textit{GO.db} package was used to load the \gls{go} database into \gls{r} \citep{Carlson2016}.
Only the human related \gls{go} terms were used in pathway enrichment analysis, and these terms were manipulated in a form which the \texttt{camera} function was able to recognise.

### 2017-01-18 thesis/misc/glossary.tex
tmp commit
Finished pathway enrichment analysis section

@@

@@

>>>>

\newglossaryentry{ontology}{
	name=Ontology,
	text=ontology,
	description={A set of concepts and categories in a subject area or domain that shows their properties and the relations between them}
}

@@

\newacronym{kegg}{KEGG}{Kyoto Encyclopedia of Genes and Genomes}

@@

\newacronym{camera}{CAMERA}{correlation adjusted mean rank gene set test}
\newacronym{ora}{ORA}{over representation analysis}
\newacronym{fcs}{FCS}{functional class scoring}
\newacronym{wmw}{WMW}{Wilcoxon-Mann-Whitney}
\newacronym{vif}{VIF}{variance inflation factor}
